---
title: "Repdata"
author: "Rui La"
date: "June 12, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

First we unzip the code and read the csv file into `df`. As the missing value of
df can be ignored, the df can be completed to complete df

```{r}
unzip("activity.zip")
df <- read.csv("activity.csv")
completedf <- df[complete.cases(df),]
head (completedf)
summary(completedf)
```

Then we can calculate the total of each day using `aggregate`

```{r pressure, echo=TRUE}
stepByDate <- aggregate(steps ~ date, data = completedf, FUN = sum)
barplot(stepByDate$steps, xlab = "date", ylab = "steps", 
        names.arg = stepByDate$date)

dailymean <- aggregate(steps ~ date, data = completedf, FUN = mean)
dailymedian <- aggregate(steps ~date, data = completedf, FUN = median)
mmdaily <- merge(dailymean, dailymedian, by.x = "date", by.y = "date")

##stepstatis <- data.frame(c)
```

Mean total number of steps is 

```{r}
mean (stepByDate$steps)
```

Median total number of steps is 

```{r}
median (stepByDate$steps)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent 
printing of the R code that generated the plot.
